\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{graphicx}

% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{\large Report on "Theory of Mind May Have Spontaneously Emerged in Large Language Models" \\
\normalsize Paper Report as Part of the "Current Topics of Computational Social Science" Seminar}

%
\titlerunning{Report on "ToM May Have Spontaneously Emerged in LLMS"}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Taline Kehlenbach}
%
\authorrunning{T. Kehlenbach}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{RWTH Aachen}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This report summarises, questions and criticises the paper "Theory of Mind May Have Spontaneously Emerged in Large Language Models" by Kosinski

\keywords{Artificial Intelligence  \and Theory of Mind \and Language Model}
\end{abstract}
%
%
%

\input{text/introduction.tex}

\input{text/related_work.tex}

\input{text/methods.tex}

\input{text/results_and_discussion.tex}

\input{text/conclusions_and_implications.tex}

\input{text/reviewer_perspective.tex}

\input{text/future_work.tex}

\subsubsection{Acknowledgements} Thanks to Professor Kosinski for answering some of my questions regarding his work and to Professor Wagner for assisting me during the seminar and writing of this paper.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%

%
\bibliographystyle{splncs04}
\bibliography{text/references}

% Bibliography
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}
