\section{Results and Discussion}
%in this section, the results of the research are presented, and how they are related to the problem under study and to what it was known until date.
The results of the first and second study show that GPT-3.5 correctly answers the two example tasks with almost 100\% probability for choosing the correct answer in each prompt. Furthermore the development of answer probabilities when given the task descriptions line by line shows that the model has no problem understanding reality i.e. it answers the first prompt correctly according to the information currently at hand. Interestingly, when given the third prompt after each line of the task description the model also seems to be able to predict the false belief of Sam in study 1 or John in study 2. For example, the model would predict that John would look for the cat in the correct locations after having witnessed the cat's transfer but would search for it in the wrong location if the pet got moved during his absence. For the Unexpected Contents Task the prediction of the correct content does not change even when the faulty label is introduced however the prediction of belief switches from the actual content to the one described on the label as the fact that the actual contents are unknown and imperceivable to the person is introduced. It is interesting to note that the prompts regarding the actual state of reality in both tasks are always answered with 100\% certainty whereas the prompts regarding false beliefs almost always have a probability below 100\% and go as low as 82\% in one case. As for the results using scrambled versions of the tasks the model only solved 6\% of the Unexpected Contents Tasks and 11\% of the Unexpected Transfer Tasks correctly, proving that the order of the information is crucial for the model's ability to pass the chosen tasks.

Regarding study 3 the results are summarised in table \ref{study3}. One can clearly see that the performance of a model in false-belief tasks rises with parameter size and therefore the most recent models GPT-3.5 and GPT-4 outperform the older and smaller models by far. Kosinski relies on the work of Wellman et al. \cite{tom_children_2001} for a comparison of these performances to that of children in different age groups. This places 3.5-year-old children at a performance of 43\% and seven-year-old children at a performance of approximately 90\%. Kosinski also argues that the tasks the models had to solve were harder than the original tasks that were designed for direct interviews with children, often using visual aides such as puppets and also having the model complete prompts instead of answering yes-or-no questions.\cite{kosinski}

\begin{table}
\caption{Percentage of correctly solved false-belief tasks for all models for study 3 on both task types including the year of the model release and parameter count \cite{kosinski}}\label{study3}
\begin{tabular}{|l|l|l|l|l|}
\hline
Model &  Month/Year & Size & Unexpected Contents& Unexpected Transfer\\
\hline
GPT-4 & 03/23 & unknown & 95\% & 100\%\\
GPT-3.5 & 11/22 & 175B & 85\% & 95\%\\
GPT-3 (davinci-200) & 01/22 & 175B & 70\% & 70\%\\
BLOOM & 06/22 & 176B & 40\% & 45\%\\
GPT-3 (davinci-001) & 05/20 & 175B & 40\% & 35\%\\
GPT-3 (curie-001) & 05/20 & 6.7B & 5\% & 5\%\\
GPT-2 (XL) & 02/19 & 1.5B & 5\% & 5\%\\
GPT-3 (babbage-001) & 05/20 & 1.3B & 5\% & 5\%\\
GPT-3 (ada-001) & 05/20 & 350M & 5\% & 5\%\\
GPT-1 & 06/18 & 117M & 5\% & 5\%\\
\hline
\end{tabular}
\end{table}